Structured Versus Decorated Cospans

### 2020-12-18 cospans.tex
inclusions into sums are iota
tiny
tweaked comments about \cref{defn:monoidal_double_category} in Theorem 2.2

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/17

@@

(B) edge node [below] {$j_m$} (F)
(D) edge node [below] {$j_{n}$} (F)

@@

Lastly, according to \cref{defn:monoidal_double_category} we construct two globular 2-isomorphisms $(M_2 \otimes N_2)\odot (M_1 \otimes N_1) \simrightarrow(M_2\odot M_1) \otimes (N_2\odot N_1)$ and $U_{a + b} \simrightarrow U_a \otimes U_b$ that express compatibility of the tensor with horizontal composition and units. For any appropriate four decorated cospans

@@

There is a much simpler proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.  In this case we show, in the proof of that theorem, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.   We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have shown independently obeys the axioms of symmetric monoidal double category (see \cref{thm:SC}).  It follows that $F \lCsp$ is a symmetric monoidal category.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/18

@@

(B) edge node [below] {$\iota_m$} (F)
(D) edge node [below] {$\iota_{n}$} (F)

@@

Lastly, according to \cref{defn:monoidal_double_category} we need to construct two globular 2-isomorphisms $(M_2 \otimes N_2)\odot (M_1 \otimes N_1) \simrightarrow(M_2\odot M_1) \otimes (N_2\odot N_1)$ and $U_{a + b} \simrightarrow U_a \otimes U_b$ that express compatibility of the tensor product with horizontal composition and units. For any appropriate four decorated cospans

@@

There is a much simpler proof of the above theorem when the hypothesis of \cref{thm:equiv} hold.  In this case we show, in the proof of that theorem, that the decorated cospan double category $F \lCsp$ is isomorphic to a certain double category ${}_L \lCsp(\inta  F)$ constructed using \emph{structured} cospans.   We also show that under this isomorphism, all the symmetric monoidal structure of $F \lCsp$---the tensor product, associator, etc.---matches that for  ${}_L \lCsp(\inta  F)$, which we have shown independently obeys the axioms of symmetric monoidal double category (see \cref{thm:SC}).  It follows that $F \lCsp$ is a symmetric monoidal double category.
